---
title: "Sqlite benchmarking report"
author: "Anna Krystalli"
date: "08/12/2017"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

***

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo = F}
library(tidyverse)

load_data <- function(dir = paste0(here::here(), "/out")) { 
 list.files(dir, full.names = T) %>% lapply(read_csv) %>%
   dplyr::bind_rows()
}

df <- load_data()
```

The code in [**`test_db`**](https://github.com/annakrystalli/sqlite_benchmark/blob/master/test-db.R) was benchmarked under a number of different scenarios. 

Briefly:

- it builds a sqlite database from the complete novels of Jane Austen (accessed through the `janeaustenr` package) (not timed), replicated `test_size` times *(`r unique(df$test_size)`)*. (see function [`create_testdb`](https://github.com/annakrystalli/sqlite_benchmark/blob/cf0aa52f2496bb6996ed3be413b5c78698eafc8e/R/functions.R#L8))
- It then **times a full inner join** of the corpus on the lexicon. (see function [`test_sqlite_io`](https://github.com/annakrystalli/sqlite_benchmark/blob/cf0aa52f2496bb6996ed3be413b5c78698eafc8e/R/functions.R#L80))



The analysis was either run locally or on sharc, and tested the i/o speed of a variety of storage location, **local**, **smb**, **sharc_data** and **sharc_scratch**, by varying the location the db was written and read from.




```{r, fig.width=10, fig.height=5, echo=FALSE}
p <- df %>% 
    ggplot(aes(test_size, time_elapsed, group = test_case, color = test_case)) +
    geom_path() +
    geom_point()

p %>% plotly::ggplotly()
```

